Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/related-work.tex
fixed bugs in Once/Since defs; added details to comparison with the INRIA work in Related Work

There is a fully verified compiler that takes Lustre and turns it into a binary executable that is specified and verified in Coq \cite{10.1145/3140587.3062358}. The key is in combining infinite sequences of data-flow models with incremental manipulation of memories akin to an imperative model. CompCert is used on the backend to create the final rendered executable.

>>>>

There is a fully verified compiler that takes Lustre and turns it into
a binary executable that is specified and verified in
Coq \cite{10.1145/3140587.3062358}. The key is in combining infinite
sequences of data-flow models with incremental manipulation of
memories akin to an imperative model. CompCert is used on the backend
to create the final rendered executable. The work is quite similar to
ours in providing a verified compilation chain from Lustre. However,
there are significant differences: first, they tackle a more
comprehensive subset of Lustre than our work. We have been able to
work effectively with a relatively simple core language, \eg, without
\emph{clocking} features, and this aligns with our contract language, so that, as well as generating behaviorally equivalent code, we also can show that the generated code meets a logical specification that is a leaf-level claim in a system-wide correctness argument conducted by compositional reasoning in AGREE.
